### 2021-11-18 text/outline/draft.tex
add sim spec 1

Our work makes two main contributions. First, we conduct a careful study of the thresholding method. Notably, we demonstrate on real data that the thresholding method exhibits attenuation bias and a bias-variance tradeoff as a function of the selected threshold, and we recover these phenomena in precise mathematical terms in an idealized Gaussian model. \blue{Second, we introduce a new method, GLM-EIV (generalized linear model with errors-in-variables), for single-cell CRISPR screen analysis. GLM-EIV generalizes the classical errors-in-variables model to response distributions and sources of measurement error that are exponential family-distributed. In doing so, GLM-EIV is able to implicitly estimate the probability that each cell was perturbed, obviating the need to explicitly impute perturbation assignments via thresholding or another heuristic.} Theoretical analyses and simulation studies indicate that GLM-EIV outperforms the thresholding method in large regions of the parameter space.

@@

\begin{figure}
	\centering
	\includegraphics[width=1\linewidth]{../../figures/analysis_challenges/plot.pdf}
	\caption{\textbf{Experimental design and analysis challenges}: \textbf{a,} Experimental design. For a given perturbation (e.g., the perturbation indicated in blue), we partition the cells into two groups: perturbed and unperturbed. Next, for a given gene, we conduct a differential expression analysis across the two groups, yielding an estimate of the impact of the given perturbation on the given gene. \textbf{b,} DAG representing all variables in the system. The perturbation (latent) impacts both gene expression and gRNA expression; technical factors act as confounders, also impacting gene and gRNA expression. The target of estimation is the effect of the perturbation on gene expression. \textbf{c,} Schematic illustrating the ``background read'' phenomenon. Due to errors in the sequencing process, unperturbed cells exhibit a nonzero gRNA count distribution (bottom). The target of estimation is the change in mean gene expression in response to the perturbation (top). \textbf{d}, Example data on four cells for a given perturbation-gene pair. Note that (i) the perturbation is unobserved, and (ii) the gene and gRNA data are discrete counts.}
	\label{analysis_challenges}
\end{figure}

>>>>

Our work makes two main contributions. First, we conduct a careful study of the thresholding method. Notably, we demonstrate on real data that the thresholding method exhibits attenuation bias and a bias-variance tradeoff as a function of the selected threshold, and we recover these phenomena in precise mathematical terms in an idealized Gaussian setting. \blue{Second, we introduce a new method, GLM-EIV (generalized linear model with errors-in-variables), for single-cell CRISPR screen analysis. GLM-EIV generalizes the classical errors-in-variables model to response distributions and sources of measurement error that are exponential family-distributed. GLM-EIV thereby implicitly estimates the probability that each cell was perturbed, obviating the need to explicitly impute perturbation assignments via thresholding or another heuristic.} Theoretical analyses and simulation studies indicate that GLM-EIV outperforms the thresholding method in large regions of the parameter space.

@@

\begin{figure}
	\centering
	\includegraphics[width=1\linewidth]{../../figures/analysis_challenges/plot.pdf}
	\caption{\textbf{Experimental design and analysis challenges}: \textbf{a,} Experimental design. For a given perturbation (e.g., the perturbation indicated in blue), we partition the cells into two groups: perturbed and unperturbed. Next, for a given gene, we conduct a differential expression analysis across the two groups, yielding an estimate of the impact of the given perturbation on the given gene. \textbf{b,} DAG representing all variables in the system. The perturbation (latent) impacts both gene expression and gRNA expression; technical factors act as confounders, also impacting gene and gRNA expression. The target of estimation is the effect of the perturbation on gene expression. \textbf{c,} Schematic illustrating the ``background read'' phenomenon. Due to errors in the sequencing and alignment processes, unperturbed cells exhibit a nonzero gRNA count distribution (bottom). The target of estimation is the change in mean gene expression in response to the perturbation (top). \textbf{d}, Example data on four cells for a given perturbation-gene pair. Note that (i) the perturbation is unobserved, and (ii) the gene and gRNA data are discrete counts.}
	\label{analysis_challenges}
\end{figure}
